pirouette: the error BEAST2 makes in inferring a phylogeny

### 2019-02-21 article.tex
Add experiment setup, progress https://github.com/richelbilderbeek/pirouette/issues/58

\begin{lstlisting}[language=R, floatplacement=H, frame=single]
experiments <- list(create_experiment())
\end{lstlisting}

@@

A third research question that \verb;pirouette; answers is:
What is the error BEAST2 makes from a phylogeny 
picking the best inference model, compared to the background noise?

The following settings are the same as in the previous section:
phylogeny (listing \ref{lst:unknown_phylogeny}), alignment parameters, inference model selection,
shared inference parameters and error measuring parameters 
\richel{TODO: add ref to code}

This time, we are interested in creating a twin tree. A twin tree
has the same topology as the given tree, yet its branch lengths follow
an idealized 
\giovanni{
  I don't think this is true. A twin tree is generated randomly. 
  If we use the method "maxlikelihood" (see the function "createbdtree") 
  the tree will be chosen in such a way it will maximizing the likelihood 
  given the parameters we estimated from the original tree, 
  but I would not call it "idealized". Furthermore I think it's not obvious to 
  use the "maxlikelihood" method, as in general the "ideal" scenario should be 
  established using a distribution of trees. A single tree is always the result 
  of a stochastic process.
}
\richel{we'll discuss this today} 
birth-death distribution. Creating a twinning parameter is easy,
as it has sensible default settings:

@@

\begin{lstlisting}[language=R, floatplacement=H, frame=single]
errors <- pir_run(
  phylogeny,
  twinning_params = twinning_params,
  alignment_params = alignment_params,
  model_select_params = model_select_param
)
\end{lstlisting}

@@

\begin{figure}[h]
  \includegraphics[width=\textwidth]{figure_4.png}
  \caption{
    The error BEAST2 makes from a phylogeny 
    picking the best inference model, compared to the background noise?
    Here, the twin column shows the error BEAST2 makes on an idealized
    tree, to measure the noise, which is the minimal error. 
    \giovanni{again, I don't believe that using an "idealized" tree is the best 
      thing to do. I would rather use more "true trees".}
    \richel{we'll discuss this today}
  }
\end{figure}

>>>>

\begin{lstlisting}[
  language=R, 
  floatplacement=H, frame=single,
  label = {lst:create_generative_experiment},
  caption = {
    Create a default experiment. This default experiment is
    for a generative model, that is always run, without its evidence measured,
    assuming a JC, strict, Yule inference model
  }
]
experiments <- list(create_experiment())
\end{lstlisting}

@@

A third research question that \verb;pirouette; answers is:
What is the error BEAST2 makes from a phylogeny, 
when hand-picking an inference model, compared to the background noise?

The following settings are the same as in the previous section:
phylogeny (listing \ref{lst:unknown_phylogeny}), 
alignment parameters (listing \ref{lst:create_alignment}), 
experiments (listing \ref{lst:create_generative_experiment})
BEAST2 inference and error measuring parameters.

This time, we are interested in creating a twin tree. A twin tree
has the same topology as the given tree, yet its branch lengths follow
a distribution as such that the BEAST2 error will be 
close to \richel{'close to' is a bit weasly, but currently it is true}
its minimal error.
Creating a twinning parameter is easy,
as it has sensible default settings:

@@

\begin{lstlisting}[language=R, floatplacement=H, frame=single]
pir_params <- create_pir_params(
  alignment_params = alignment_params,
  experiments = experiments,
  twinning_params = twinning_params
)
\end{lstlisting}

Running:

@@

\begin{figure}[h]
  \includegraphics[width=\textwidth]{figure_4.png}
  \caption{
    The error BEAST2 makes from a phylogeny 
    picking the best inference model, compared to the background noise?
    Here, the twin column shows the error BEAST2 makes on an idealized
    tree, to measure the noise, which is the minimal error. 
  }
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Other examples}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

There are many other examples that can be found in the \verb;pirouette; 
documentation.
